---
title: "Hotel lightgbm"
author: "WY"
date: "`r Sys.Date()`"
output: html_document
---

# Init
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# pkgs <- 
#   c("bonsai", "Cubist", "doParallel", "earth", "embed", "finetune", 
#     "forested", "lightgbm", "lme4", "parallelly", "plumber", "probably", 
#     "ranger", "rpart", "rpart.plot", "rules", "splines2", "stacks", 
#     "text2vec", "textrecipes", "tidymodels", "vetiver")
# 
# install.packages(pkgs)
# rlang::check_installed("dials", version = "1.3.0")

library(tidymodels)

# Max's usual settings: 
tidymodels_prefer()
theme_set(theme_bw())
options(
  pillar.advice = FALSE, 
  pillar.min_title_chars = Inf
)

# Add another package:
library(textrecipes)
reg_metrics <- metric_set(mae, rsq)

```

# Hotel data
```{r}

data(hotel_rates)
set.seed(295)
hotel_rates <- 
  hotel_rates %>% 
  sample_n(5000) %>% 
  arrange(arrival_date) %>% 
  select(-arrival_date) %>% 
  mutate(
    company = factor(as.character(company)),
    country = factor(as.character(country)),
    agent = factor(as.character(agent))
  )
```

## Hotel data columns
```{r}
names(hotel_rates)
#>  [1] "avg_price_per_room"             "lead_time"                     
#>  [3] "stays_in_weekend_nights"        "stays_in_week_nights"          
#>  [5] "adults"                         "children"                      
#>  [7] "babies"                         "meal"                          
#>  [9] "country"                        "market_segment"                
#> [11] "distribution_channel"           "is_repeated_guest"             
#> [13] "previous_cancellations"         "previous_bookings_not_canceled"
#> [15] "reserved_room_type"             "assigned_room_type"            
#> [17] "booking_changes"                "agent"                         
#> [19] "company"                        "days_in_waiting_list"          
#> [21] "customer_type"                  "required_car_parking_spaces"   
#> [23] "total_of_special_requests"      "arrival_date_num"              
#> [25] "near_christmas"                 "near_new_years"                
#> [27] "historical_adr"
```
## eda outcome average price per month
```{r}
hotel_rates|>select(avg_price_per_room) |>skimr::skim()
```

## mutate
```{r}
data(hotel_rates)
set.seed(295)
hotel_rates <- 
  hotel_rates %>% 
  sample_n(5000) %>% 
  arrange(arrival_date) %>% 
  select(-arrival_date) %>% 
  mutate(
    company = factor(as.character(company)),
    country = factor(as.character(country)),
    agent = factor(as.character(agent))
  )
```


# Data splitting strategy

## Data Spending
Let’s split the data into a training set (75%) and testing set (25%) using stratification:
```{r}
set.seed(4028)
hotel_split <- initial_split(hotel_rates, strata = avg_price_per_room)

hotel_train <- training(hotel_split)
hotel_test <- testing(hotel_split)

set.seed(472)
hotel_rs <- vfold_cv(hotel_train, strata = avg_price_per_room)

```
We’ll go from here and create a set of resamples to use for model assessments.

# Resampling Strategy

## Resampling Strategy
We’ll use simple 10-fold cross-validation (stratified sampling):
```{r}
set.seed(472)
hotel_rs <- vfold_cv(hotel_train, strata = avg_price_per_room)
hotel_rs
#> #  10-fold cross-validation using stratification 
#> # A tibble: 10 × 2
#>    splits             id    
#>    <list>             <chr> 
#>  1 <split [3372/377]> Fold01
#>  2 <split [3373/376]> Fold02
#>  3 <split [3373/376]> Fold03
#>  4 <split [3373/376]> Fold04
#>  5 <split [3373/376]> Fold05
#>  6 <split [3374/375]> Fold06
#>  7 <split [3375/374]> Fold07
#>  8 <split [3376/373]> Fold08
#>  9 <split [3376/373]> Fold09
#> 10 <split [3376/373]> Fold10
```
# Prepare your data for modeling
The recipes package is an extensible framework for pipeable sequences of preprocessing and feature engineering steps.
Statistical parameters for the steps can be estimated from an initial data set and then applied to other data sets.
The resulting processed output can be used as inputs for statistical or machine learning models.
## A first recipe
```{r}
hotel_rec <- 
  recipe(avg_price_per_room ~ ., data = hotel_train)

```
## A first recipe
```{r}
summary(hotel_rec)
#> # A tibble: 27 × 4#>    variable                type      role      source  
#>    <chr>                   <list>    <chr>     <chr>   
#>  1 lead_time               <chr [2]> predictor original
#>  2 stays_in_weekend_nights <chr [2]> predictor original
#>  3 stays_in_week_nights    <chr [2]> predictor original
#>  4 adults                  <chr [2]> predictor original
#>  5 children                <chr [2]> predictor original
#>  6 babies                  <chr [2]> predictor original
#>  7 meal                    <chr [3]> predictor original
#>  8 country                 <chr [3]> predictor original
#>  9 market_segment          <chr [3]> predictor original
#> 10 distribution_channel    <chr [3]> predictor original
#> # ℹ 17 more rows
```
## Create indicator variables
```{r}

hotel_rec <- 
  recipe(avg_price_per_room ~ ., data = hotel_train) %>% 
  step_dummy(all_nominal_predictors())

```

## Filter out constant columns

```{r}
hotel_rec <- 
  recipe(avg_price_per_room ~ ., data = hotel_train) %>% 
  step_dummy(all_nominal_predictors()) %>% 
  step_zv(all_predictors())
```

In case there is a factor level that was never observed in the training data (resulting in a column of all 0s), we can delete any zero-variance predictors that have a single unique value.

Note that the selector chooses all columns with a role of “predictor”

## Normalization
```{r}
hotel_rec <- 
  recipe(avg_price_per_room ~ ., data = hotel_train) %>% 
  step_dummy(all_nominal_predictors()) %>% 
  step_zv(all_predictors()) %>% 
  step_normalize(all_numeric_predictors())
```

This centers and scales the numeric predictors.

The recipe will use the training set to estimate the means and standard deviations of the data.

All data the recipe is applied to will be normalized using those statistics (there is no re-estimation).

## Reduce correlation

```{r}

hotel_rec <- 
  recipe(avg_price_per_room ~ ., data = hotel_train) %>% 
  step_dummy(all_nominal_predictors()) %>% 
  step_zv(all_predictors()) %>% 
  step_normalize(all_numeric_predictors()) %>% 
  step_corr(all_numeric_predictors(), threshold = 0.9)

```
## Other possible steps - pca
```{r}
hotel_rec <- 
  recipe(avg_price_per_room ~ ., data = hotel_train) %>% 
  step_dummy(all_nominal_predictors()) %>% 
  step_zv(all_predictors()) %>% 
  step_normalize(all_numeric_predictors()) %>% 
  step_pca(all_numeric_predictors())
```
## Other possible steps - umap
```{r}
hotel_rec <- 
  recipe(avg_price_per_room ~ ., data = hotel_train) %>% 
  step_dummy(all_nominal_predictors()) %>% 
  step_zv(all_predictors()) %>% 
  step_normalize(all_numeric_predictors()) %>% 
  embed::step_umap(all_numeric_predictors(), outcome = vars(avg_price_per_room))
```
A fancy machine learning supervised dimension reduction technique called UMAP…

Note that this uses the outcome, and it is from an extension package

## Other possible steps
```{r}
hotel_rec <- 
  recipe(avg_price_per_room ~ ., data = hotel_train) %>% 
  step_dummy(all_nominal_predictors()) %>% 
  step_zv(all_predictors()) %>% 
  step_normalize(all_numeric_predictors()) %>% 
  step_spline_natural(arrival_date_num, deg_free = 10)
```
Nonlinear transforms like natural splines, and so on! https://aml4td.org/chapters/interactions-nonlinear.html#sec-splines

## Minimal recipe
```{r}
hotel_indicators <-
  recipe(avg_price_per_room ~ ., data = hotel_train) %>% 
  step_YeoJohnson(lead_time) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_zv(all_predictors()) %>% 
  step_spline_natural(arrival_date_num, deg_free = 10)
```

# Measuring Performance
We’ll compute two measures: mean absolute error and the coefficient of determination (a.k.a \(R^2\)).

\[\begin{align} MAE &= \frac{1}{n}\sum_{i=1}^n |y_i - \hat{y}_i| \notag \\ R^2 &= cor(y_i, \hat{y}_i)^2 \end{align}\]

The focus will be on MAE for parameter optimization. We’ll use a metric set to compute these:
```{r}

reg_metrics <- metric_set(mae, rsq)
```

# Using a workflow
```{r}
set.seed(9)

hotel_lm_wflow <-
  workflow() %>%
  add_recipe(hotel_indicators) %>%
  add_model(linear_reg())
 
ctrl <- control_resamples(save_pred = TRUE)
hotel_lm_res <-
  hotel_lm_wflow %>%
  fit_resamples(hotel_rs, control = ctrl, metrics = reg_metrics)

collect_metrics(hotel_lm_res)
#> # A tibble: 2 × 6
#>   .metric .estimator   mean     n std_err .config             
#>   <chr>   <chr>       <dbl> <int>   <dbl> <chr>               
#> 1 mae     standard   16.6      10 0.214   Preprocessor1_Model1
#> 2 rsq     standard    0.884    10 0.00339 Preprocessor1_Model1
```
# Holdout predictions
```{r}
# Since we used `save_pred = TRUE`
lm_cv_pred <- collect_predictions(hotel_lm_res)
lm_cv_pred %>% print(n = 7)
#> # A tibble: 3,749 × 5
#>   .pred id      .row avg_price_per_room .config             
#>   <dbl> <chr>  <int>              <dbl> <chr>               
#> 1  75.1 Fold01    20                 40 Preprocessor1_Model1
#> 2  49.3 Fold01    28                 54 Preprocessor1_Model1
#> 3  64.9 Fold01    45                 50 Preprocessor1_Model1
#> 4  52.8 Fold01    49                 42 Preprocessor1_Model1
#> 5  48.6 Fold01    61                 49 Preprocessor1_Model1
#> 6  29.8 Fold01    66                 40 Preprocessor1_Model1
#> 7  36.9 Fold01    88                 49 Preprocessor1_Model1
#> # ℹ 3,742 more rows
```
## Calibration Plot
```{r}
library(probably)

cal_plot_regression(hotel_lm_res)

```

# What do we do with the agent and company data?
There are 98 unique agent values and 100 unique companies in our training set. How can we include this information in our model?
```{r}

```

We could:

make the full set of indicator variables 😳

lump agents and companies that rarely occur into an “other” group

use feature hashing to create a smaller set of indicator variables

use effect encoding to replace the agent and company columns with the estimated effect of that predictor (in the extra materials)

Per-agent statistics




## Collapsing factor levels
There is a recipe step that will redefine factor levels based on their frequency in the training set:
```{r}
hotel_other_rec <-
  recipe(avg_price_per_room ~ ., data = hotel_train) %>% 
  step_YeoJohnson(lead_time) %>%
  step_other(agent, threshold = 0.001) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_zv(all_predictors()) %>% 
  step_spline_natural(arrival_date_num, deg_free = 10)
```

Using this code, 34 agents (out of 98) were collapsed into “other” based on the training set.

We could try to optimize the threshold for collapsing (see the next set of slides on model tuning).

Does othering help?
```{r}
hotel_other_wflow <-
  hotel_lm_wflow %>%
  update_recipe(hotel_other_rec)

hotel_other_res <-
  hotel_other_wflow %>%
  fit_resamples(hotel_rs, control = ctrl, metrics = reg_metrics)

collect_metrics(hotel_other_res)
#> # A tibble: 2 × 6
#>   .metric .estimator   mean     n std_err .config             
#>   <chr>   <chr>       <dbl> <int>   <dbl> <chr>               
#> 1 mae     standard   16.7      10 0.213   Preprocessor1_Model1
#> 2 rsq     standard    0.884    10 0.00341 Preprocessor1_Model1
```

About the same MAE and much faster to complete.

Now let’s look at a more sophisticated tool called effect feature hashing.

## Feature Hashing
Between agent and company, simple dummy variables would create 198 new columns (that are mostly zeros).

Another option is to have a binary indicator that combines some levels of these variables.

Feature hashing (for more see FES, SMLTAR, TMwR, and aml4td):

uses the character values of the levels
converts them to integer hash values
uses the integers to assign them to a specific indicator column.
### Feature Hashing
Suppose we want to use 32 indicator variables for agent.

For a agent with value “Max_Kuhn”, a hashing function converts it to an integer (say 210397726).

To assign it to one of the 32 columns, we would use modular arithmetic to assign it to a column:
```{r}
# For "Max_Kuhn" put a '1' in column: 
210397726 %% 32
#> [1] 30
```

### Feature Hashing Pros
The procedure will automatically work on new values of the predictors.
It is fast.
“Signed” hashes add a sign to help avoid aliasing.
### Feature Hashing Cons
There is no real logic behind which factor levels are combined.
We don’t know how many columns to add (more in the next section).
Some columns may have all zeros.
If a indicator column is important to the model, we can’t easily determine why.
The signed hash make it slightly more possible to differentiate between confounded levels

### Feature Hashing in recipes
The textrecipes package has a step that can be added to the recipe:
```{r}
library(textrecipes)

hash_rec <-
  recipe(avg_price_per_room ~ ., data = hotel_train) %>%
  step_YeoJohnson(lead_time) %>%
  # Defaults to 32 signed indicator columns
  step_dummy_hash(agent) %>%
  step_dummy_hash(company) %>%
  # Regular indicators for the others
  step_dummy(all_nominal_predictors()) %>% 
  step_zv(all_predictors())

# hash_rec <-
#   recipe(avg_price_per_room ~ ., data = hotel_train) %>%
#   step_YeoJohnson(lead_time) %>%
#   # Defaults to 32 signed indicator columns
#   step_dummy_hash(agent) %>%
#   step_dummy_hash(company) %>%
#   # Regular indicators for the others
#   step_dummy(all_nominal_predictors()) %>% 
#   step_zv(all_predictors()) %>% 
#   step_spline_natural(arrival_date_num, deg_free = 10)

hotel_hash_wflow <-
  hotel_lm_wflow %>%
  update_recipe(hash_rec)
```

### Feature Hashing in recipes
```{r}


hotel_hash_res <-
  hotel_hash_wflow %>%
  fit_resamples(hotel_rs, control = ctrl, metrics = reg_metrics)

collect_metrics(hotel_hash_res)
#> # A tibble: 2 × 6
#>   .metric .estimator   mean     n std_err .config             
#>   <chr>   <chr>       <dbl> <int>   <dbl> <chr>               
#> 1 mae     standard   16.7      10 0.239   Preprocessor1_Model1
#> 2 rsq     standard    0.884    10 0.00324 Preprocessor1_Model1

```


About the same performance but now we can handle new values.

## Debugging a recipe

Typically, you will want to use a workflow to estimate and apply a recipe.
If you have an error and need to debug your recipe, the original recipe object (e.g. hash_rec) can be estimated manually with a function called prep(). It is analogous to fit(). See TMwR section 16.4
Another function (bake()) is analogous to predict(), and gives you the processed data back.
The tidy() function can be used to get specific results from the recipe.
### Example
```{r}

hash_rec_fit <- prep(hash_rec)

# Get the transformation coefficient
tidy(hash_rec_fit, number = 1)

# Get the processed data
bake(hash_rec_fit, hotel_train %>% slice(1:3), contains("_agent_"))
```
## More on recipes
Once fit() is called on a workflow, changing the model does not re-fit the recipe.
A list of all known steps is at https://www.tidymodels.org/find/recipes/.
Some steps can be skipped when using predict().
The order of the steps matters.


Optimizing Models via Tuning Parameters
# Tuning parameters
Some model or preprocessing parameters cannot be estimated directly from the data.

Some examples:

### Tree depth in decision trees
### Number of neighbors in a K-nearest neighbor model
### Activation function in neural networks?
Sigmoidal functions, ReLu, etc.

Yes, it is a tuning parameter. ✅

### Number of feature hashing columns to generate?
Yes, it is a tuning parameter. ✅

### Bayesian priors for model parameters?
Hmmmm, probably not. These are based on prior belief. ❌

### The random seed?
Nope. It is not. ❌

## Optimize tuning parameters
- Try different values and measure their performance.
- Find good values for these parameters.
- Once the value(s) of the parameter(s) are determined, a model can be finalized by fitting the model to the entire training set.

## Tagging parameters for tuning
With tidymodels, you can mark the parameters that you want to optimize with a value of tune().
The function itself just returns… itself:
```{r}


tune()
#> tune()
str(tune())
#>  language tune()

# optionally add a label
tune("I hope that the workshop is going well")
#> tune("I hope that the workshop is going well")

```
or example…

## Optimizing the hash features
Our new recipe is:
```{r}
hash_rec <-
  recipe(avg_price_per_room ~ ., data = hotel_train) %>%
  step_YeoJohnson(lead_time) %>%
  step_dummy_hash(agent,   num_terms = tune("agent hash")) %>%
  step_dummy_hash(company, num_terms = tune("company hash")) %>%
  step_zv(all_predictors())

```

We will be using a tree-based model in a minute.

The other categorical predictors are left as-is.
That’s why there is no step_dummy().


# Boosted Trees
These are popular ensemble methods that build a sequence of tree models.



Each tree uses the results of the previous tree to better predict samples, especially those that have been poorly predicted.



Each tree in the ensemble is saved and new samples are predicted using a weighted average of the votes of each tree in the ensemble.



We’ll focus on the popular lightgbm implementation.

## Boosted Tree Tuning Parameters
Some possible parameters:

mtry: The number of predictors randomly sampled at each split (in \([1, ncol(x)]\) or \((0, 1]\)).
trees: The number of trees (\([1, \infty]\), but usually up to thousands)
min_n: The number of samples needed to further split (\([1, n]\)).
learn_rate: The rate that each tree adapts from previous iterations (\((0, \infty]\), usual maximum is 0.1).
stop_iter: The number of iterations of boosting where no improvement was shown before stopping (\([1, trees]\))
Boosted Tree Tuning Parameters
TBH it is usually not difficult to optimize these models.



Often, there are multiple candidate tuning parameter combinations that have very good results.



To demonstrate simple concepts, we’ll look at optimizing the number of trees in the ensemble (between 1 and 100) and the learning rate (\(10^{-5}\) to \(10^{-1}\)).

Boosted Tree Tuning Parameters
We’ll need to load the bonsai package. This has the information needed to use lightgbm
```{r}
library(bonsai)
lgbm_spec <- 
  boost_tree(trees = tune(), learn_rate = tune()) %>% 
  set_mode("regression") %>% 
  set_engine("lightgbm", num_threads = 1)

lgbm_wflow <- workflow(hash_rec, lgbm_spec)
```

### Optimize tuning parameters
The main two strategies for optimization are:

# Grid search 💠 which tests a pre-defined set of candidate values

## Iterative search 🌀 which suggests/estimates new values of candidate parameters to evaluate

Grid search
A small grid of points trying to minimize the error via learning rate:


Grid search
In reality we would probably sample the space more densely:


Iterative Search
We could start with a few points and search the space:


### Grid Search Parameters
The tidymodels framework provides pre-defined information on tuning parameters (such as their type, range, transformations, etc).

The extract_parameter_set_dials() function extracts these tuning parameters and the info.

Grids
Create your grid manually or automatically.

The grid_*() functions can make a grid.

Most basic (but very effective) way to tune models

### Different types of grids
```{r}
lgbm_wflow %>% 
  extract_parameter_set_dials()
#> Collection of 4 parameters for tuning
#> 
#>    identifier       type    object
#>         trees      trees nparam[+]
#>    learn_rate learn_rate nparam[+]
#>    agent hash  num_terms nparam[+]
#>  company hash  num_terms nparam[+]

# Individual functions: 
trees()
#> # Trees (quantitative)
#> Range: [1, 2000]
learn_rate()
#> Learning Rate (quantitative)
#> Transformer: log-10 [1e-100, Inf]
#> Range (transformed scale): [-10, -1]
```


Space-filling designs (SFD) attempt to cover the parameter space without redundant candidates. We recommend these the most.

### Create a grid
```{r}
set.seed(12)
grid <- 
  lgbm_wflow %>% 
  extract_parameter_set_dials() %>% 
  grid_space_filling(size = 25)

grid
#> # A tibble: 25 × 4
#>    trees learn_rate `agent hash` `company hash`
#>    <int>      <dbl>        <int>          <int>
#>  1     1   7.50e- 6          574            574
#>  2    84   1.78e- 5         2048           2298
#>  3   167   5.62e-10         1824            912
#>  4   250   4.22e- 5         3250            512
#>  5   334   1.78e- 8          512           2896
#>  6   417   1.33e- 3          322           1625
#>  7   500   1   e- 1         1448           1149
#>  8   584   1   e- 7         1290            256
#>  9   667   2.37e-10          456            724
#> 10   750   1.78e- 2          645            322
#> # ℹ 15 more rows
```


Your turn


Create a grid for our tunable workflow.

Try creating a regular grid.


### Create a regular grid
```{r}
set.seed(12)
grid <- 
  lgbm_wflow %>% 
  extract_parameter_set_dials() %>% 
  grid_regular(levels = 4)

grid
#> # A tibble: 256 × 4
#>    trees   learn_rate `agent hash` `company hash`
#>    <int>        <dbl>        <int>          <int>
#>  1     1 0.0000000001          256            256
#>  2   667 0.0000000001          256            256
#>  3  1333 0.0000000001          256            256
#>  4  2000 0.0000000001          256            256
#>  5     1 0.0000001             256            256
#>  6   667 0.0000001             256            256
#>  7  1333 0.0000001             256            256
#>  8  2000 0.0000001             256            256
#>  9     1 0.0001                256            256
#> 10   667 0.0001                256            256
#> # ℹ 246 more rows
```
Your turn




What advantage would a regular grid have?

#### Update parameter ranges
```{r}

lgbm_param <- 
  lgbm_wflow %>% 
  extract_parameter_set_dials() %>% 
  update(trees = trees(c(1L, 100L)),
         learn_rate = learn_rate(c(-5, -1)))

set.seed(712)
grid <- 
  lgbm_param %>% 
  grid_space_filling(size = 25)

grid
#> # A tibble: 25 × 4
#>    trees learn_rate `agent hash` `company hash`
#>    <int>      <dbl>        <int>          <int>
#>  1     1  0.00147            574            574
#>  2     5  0.00215           2048           2298
#>  3     9  0.0000215         1824            912
#>  4    13  0.00316           3250            512
#>  5    17  0.0001             512           2896
#>  6    21  0.0147             322           1625
#>  7    25  0.1               1448           1149
#>  8    29  0.000215          1290            256
#>  9    34  0.0000147          456            724
#> 10    38  0.0464             645            322
#> # ℹ 15 more rows
```

The results
```{r}
grid %>% 
  ggplot(aes(trees, learn_rate)) +
  geom_point(size = 4) +
  scale_y_log10()

```
Note that the learning rates are uniform on the log-10 scale and this shows 2 of 4 dimensions.

Use the tune_*() functions to tune models
### Choosing tuning parameters
Let’s take our previous model and tune more parameters:
```{r}
lgbm_spec <- 
  boost_tree(trees = tune(), learn_rate = tune(),  min_n = tune()) %>% 
  set_mode("regression") %>% 
  set_engine("lightgbm", num_threads = 1)

lgbm_wflow <- workflow(hash_rec, lgbm_spec)

# Update the feature hash ranges (log-2 units)
lgbm_param <-
  lgbm_wflow %>%
  extract_parameter_set_dials() %>%
  update(`agent hash`   = num_hash(c(3, 8)),
         `company hash` = num_hash(c(3, 8)))
```

### Grid Search

```{r}
set.seed(9)
ctrl <- control_grid(save_pred = TRUE)

lgbm_res <-
  lgbm_wflow %>%
  tune_grid(
    resamples = hotel_rs,
    grid = 25,
    # The options below are not required by default
    param_info = lgbm_param, 
    control = ctrl,
    metrics = reg_metrics
  )
```

tune_grid() is representative of tuning function syntax
similar to fit_resamples()
```{r}
lgbm_res 
#> # Tuning results
#> # 10-fold cross-validation using stratification 
#> # A tibble: 10 × 5
#>    splits             id     .metrics          .notes           .predictions        
#>    <list>             <chr>  <list>            <list>           <list>              
#>  1 <split [3372/377]> Fold01 <tibble [50 × 9]> <tibble [0 × 4]> <tibble [9,425 × 9]>
#>  2 <split [3373/376]> Fold02 <tibble [50 × 9]> <tibble [0 × 4]> <tibble [9,400 × 9]>
#>  3 <split [3373/376]> Fold03 <tibble [50 × 9]> <tibble [0 × 4]> <tibble [9,400 × 9]>
#>  4 <split [3373/376]> Fold04 <tibble [50 × 9]> <tibble [0 × 4]> <tibble [9,400 × 9]>
#>  5 <split [3373/376]> Fold05 <tibble [50 × 9]> <tibble [0 × 4]> <tibble [9,400 × 9]>
#>  6 <split [3374/375]> Fold06 <tibble [50 × 9]> <tibble [0 × 4]> <tibble [9,375 × 9]>
#>  7 <split [3375/374]> Fold07 <tibble [50 × 9]> <tibble [0 × 4]> <tibble [9,350 × 9]>
#>  8 <split [3376/373]> Fold08 <tibble [50 × 9]> <tibble [0 × 4]> <tibble [9,325 × 9]>
#>  9 <split [3376/373]> Fold09 <tibble [50 × 9]> <tibble [0 × 4]> <tibble [9,325 × 9]>
#> 10 <split [3376/373]> Fold10 <tibble [50 × 9]> <tibble [0 × 4]> <tibble [9,325 × 9]>
```

Grid results
```{r}
autoplot(lgbm_res)
```
#### Tuning results 1
```{r}
collect_metrics(lgbm_res)
#> # A tibble: 50 × 11
#>    trees min_n learn_rate `agent hash` `company hash` .metric .estimator   mean     n std_err .config              
#>    <int> <int>      <dbl>        <int>          <int> <chr>   <chr>       <dbl> <int>   <dbl> <chr>                
#>  1   298    19   4.15e- 9          222             36 mae     standard   53.2      10 0.427   Preprocessor01_Model1
#>  2   298    19   4.15e- 9          222             36 rsq     standard    0.810    10 0.00686 Preprocessor01_Model1
#>  3  1394     5   5.82e- 6           28             21 mae     standard   52.9      10 0.424   Preprocessor02_Model1
#>  4  1394     5   5.82e- 6           28             21 rsq     standard    0.810    10 0.00800 Preprocessor02_Model1
#>  5   774    12   4.41e- 2           27             95 mae     standard    9.77     10 0.155   Preprocessor03_Model1
#>  6   774    12   4.41e- 2           27             95 rsq     standard    0.946    10 0.00341 Preprocessor03_Model1
#>  7  1342     7   6.84e-10           71             17 mae     standard   53.2      10 0.427   Preprocessor04_Model1
#>  8  1342     7   6.84e-10           71             17 rsq     standard    0.811    10 0.00785 Preprocessor04_Model1
#>  9   669    39   8.62e- 7          141            145 mae     standard   53.2      10 0.426   Preprocessor05_Model1
#> 10   669    39   8.62e- 7          141            145 rsq     standard    0.807    10 0.00639 Preprocessor05_Model1
#> # ℹ 40 more rows
```
#### result 2
```{r}
collect_metrics(lgbm_res, summarize = FALSE)
#> # A tibble: 500 × 10
#>    id     trees min_n    learn_rate `agent hash` `company hash` .metric .estimator .estimate .config              
#>    <chr>  <int> <int>         <dbl>        <int>          <int> <chr>   <chr>          <dbl> <chr>                
#>  1 Fold01   298    19 0.00000000415          222             36 mae     standard      51.8   Preprocessor01_Model1
#>  2 Fold01   298    19 0.00000000415          222             36 rsq     standard       0.821 Preprocessor01_Model1
#>  3 Fold02   298    19 0.00000000415          222             36 mae     standard      52.1   Preprocessor01_Model1
#>  4 Fold02   298    19 0.00000000415          222             36 rsq     standard       0.804 Preprocessor01_Model1
#>  5 Fold03   298    19 0.00000000415          222             36 mae     standard      52.2   Preprocessor01_Model1
#>  6 Fold03   298    19 0.00000000415          222             36 rsq     standard       0.786 Preprocessor01_Model1
#>  7 Fold04   298    19 0.00000000415          222             36 mae     standard      51.7   Preprocessor01_Model1
#>  8 Fold04   298    19 0.00000000415          222             36 rsq     standard       0.826 Preprocessor01_Model1
#>  9 Fold05   298    19 0.00000000415          222             36 mae     standard      55.2   Preprocessor01_Model1
#> 10 Fold05   298    19 0.00000000415          222             36 rsq     standard       0.845 Preprocessor01_Model1
#> # ℹ 490 more rows
```

## Choose a parameter combination
```{r}
show_best(lgbm_res, metric = "rsq")
#> # A tibble: 5 × 11
#>   trees min_n learn_rate `agent hash` `company hash` .metric .estimator  mean     n std_err .config              
#>   <int> <int>      <dbl>        <int>          <int> <chr>   <chr>      <dbl> <int>   <dbl> <chr>                
#> 1  1890    10    0.0159           115            174 rsq     standard   0.948    10 0.00334 Preprocessor12_Model1
#> 2   774    12    0.0441            27             95 rsq     standard   0.946    10 0.00341 Preprocessor03_Model1
#> 3  1638    36    0.0409            15            120 rsq     standard   0.945    10 0.00384 Preprocessor16_Model1
#> 4   963    23    0.00556          157             13 rsq     standard   0.937    10 0.00320 Preprocessor06_Model1
#> 5   590     5    0.00320           85             73 rsq     standard   0.908    10 0.00465 Preprocessor24_Model1
```

### Choose a parameter combination
Create your own tibble for final parameters or use one of the tune::select_*() functions:
```{r}


lgbm_best <- select_best(lgbm_res, metric = "mae")
lgbm_best
#> # A tibble: 1 × 6
#>   trees min_n learn_rate `agent hash` `company hash` .config              
#>   <int> <int>      <dbl>        <int>          <int> <chr>                
#> 1  1890    10     0.0159          115            174 Preprocessor12_Model1

```


## Checking Calibration
```{r}

library(probably)
lgbm_res %>%
  collect_predictions(
    parameters = lgbm_best
  ) %>%
  cal_plot_regression(
    truth = avg_price_per_room,
    estimate = .pred
  )
```


# Run in Parallel
Grid search, combined with resampling, requires fitting a lot of models!

These models don’t depend on one another and can be run in parallel.

We can use a parallel backend to do this:
```{r}

cores <- parallelly::availableCores(logical = FALSE)
cl <- parallel::makePSOCKcluster(cores)
doParallel::registerDoParallel(cl)

# Now call `tune_grid()`!

# Shut it down with:
foreach::registerDoSEQ()
parallel::stopCluster(cl)

```

```{r}

```


Speed-ups are fairly linear up to the number of physical cores (10 here).


Faceted on the expensiveness of preprocessing used.

## The ‘future’ of parallel processing
We have relied on the foreach package for parallel processing.

We will start the transition to using the future package in the upcoming version of the tune package (version 1.3.0).

There will be a period of backward compatibility where you can still use foreach with future via the doFuture package. After that, the transition to future will occur.

## Overall, there will be minimal changes to your code.

### Early stopping for boosted trees
We have directly optimized the number of trees as a tuning parameter.

Instead we could

Set the number of trees to a single large number.
Stop adding trees when performance gets worse.
This is known as “early stopping” and there is a parameter for that: stop_iter.

Early stopping has a potential to decrease the tuning time.

Your turn




Set trees = 2000 and tune the stop_iter parameter.

Note that you will need to regenerate lgbm_param with your new workflow!

# Racing

## First, a shameless promotion

Making Grid Search More Efficient
In the last section, we evaluated 250 models (25 candidates times 10 resamples).

We can make this go faster using parallel processing.

Also, for some models, we can fit far fewer models than the number that are being evaluated.

For boosting, a model with X trees can often predict on candidates with less than X trees.
Both of these methods can lead to enormous speed-ups.

## Model Racing
Racing is an old tool that we can use to go even faster.

Evaluate all of the candidate models but only for a few resamples.
Determine which candidates have a low probability of being selected.
Eliminate poor candidates.
Repeat with next resample (until no more resamples remain)
This can result in fitting a small number of models.

### Discarding Candidates
How do we eliminate tuning parameter combinations?

There are a few methods to do so. We’ll use one based on analysis of variance (ANOVA).

However… there is typically a large difference between resamples in the results.

#### Resampling Results (Non-Racing)
Here are some realistic (but simulated) examples of two candidate models.

An error estimate is measured for each of 10 resamples.

The lines connect resamples.
There is usually a significant resample-to-resample effect (rank corr: 0.83).



### Are Candidates Different?
One way to evaluate these models is to do a paired t-test

or a t-test on their differences matched by resamples
With \(n = 10\) resamples, the confidence interval for the difference in RMSE is (0.99, 2.8), indicating that candidate number 2 has smaller error.

### Evaluating Differences in Candidates
What if we were to have compared the candidates while we seqeuntially evaluated each resample?

👉


One candidate shows superiority when 4 resamples have been evaluated.



### Interim Analysis of Results
One version of racing uses a mixed model ANOVA to construct one-sided confidence intervals for each candidate versus the current best.

Any candidates whose bound does not include zero are discarded. Here is an animation.

The resamples are analyzed in a random order (so set the seed).



Kuhn (2014) has examples and simulations to show that the method works.

The finetune package has functions tune_race_anova() and tune_race_win_loss().

## Racing
```{r}


# Let's use a larger grid
set.seed(8945)
lgbm_grid <- 
  lgbm_param %>% 
  grid_space_filling(size = 50)

library(finetune)

set.seed(9)
lgbm_race_res <-
  lgbm_wflow %>%
  tune_race_anova(
    resamples = hotel_rs,
    grid = lgbm_grid, 
    metrics = reg_metrics
  )
```
The syntax and helper functions are extremely similar to those shown for tune_grid().

## Racing Results
```{r}


show_best(lgbm_race_res, metric = "mae")
#> # A tibble: 2 × 11
#>   trees min_n learn_rate `agent hash` `company hash` .metric .estimator  mean     n std_err .config              
#>   <int> <int>      <dbl>        <int>          <int> <chr>   <chr>      <dbl> <int>   <dbl> <chr>                
#> 1  1347     5     0.0655           66             26 mae     standard    9.64    10   0.173 Preprocessor34_Model1
#> 2   980     8     0.0429           17            135 mae     standard    9.76    10   0.164 Preprocessor25_Model1
```
### Racing Results
Only 171 models were fit (out of 500).

select_best() never considers candidate models that did not get to the end of the race.

There is a helper function to see how candidate models were removed from consideration.
```{r}


plot_race(lgbm_race_res) + 
  scale_x_continuous(breaks = pretty_breaks())
```
