---
title: "tidymodels_regression_demo"
author: "WY"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

library(tidymodels)
library(lubridate)
library(lightgbm)
library(bonsai)
library(parsnip)
library(recipes)
library(dplyr)
library(forcats)
source('etl.R')
source('utils.R')
source('insurance_rec.R')
source('mod_board.R')
init_db(do = FALSE) # when first time using it, the do parameter should be changed to TRUE as below 
# init_db(do =TRUE)
```

# 1. Introduction
```{r,cache=TRUE}
get_train() |> skimr::skim()

```

show the Premium Amount distribution
```{r}
get_train() |>select(truth=Premium.Amount)|>
  #mutate(truth=log1p(truth))|>
  ggplot(aes(x=truth)) +
  geom_histogram(bins = 100, fill = "blue", color = "black") +
  labs(title = 'Premium Amount distribution plot with log1p',x='Premium Amount')+
  scale_x_continuous(trans = "log1p", breaks = c(0, 100,250,500,1000, 2000, 4000, 6000) 
                     #, labels = c(0, 1, 2, 5, 10) 
                     )+
  theme_classic()
```


# 2.Regression Model improve step by step
## 2.1 frame work


## 2.2models
### -0). V0 init- guest 1102.545
```{r}

get_vmod_v0 <- function(){
  
  avg_value <- 
    get_sample()|>
    summarize(avg_value=mean(`Premium.Amount`))|>
    pull(avg_value)
  
  df <- get_train() |>
    select(truth='Premium.Amount')|>
    mutate(estimate=avg_value)|>
    collect()
  
  rcp <- 
    recipes::recipe(truth ~ estimate, data=df)
  
    # Get the call stack
  
  current_function_name <-
    sys.calls() |>
    as.character()|> 
    gsub('()','',x=_,fixed=T)
  
  vmod <- 
    get_fit_wf(rcp,
               data = df,
               name= current_function_name,
               description='interception 1102.545')
  return(vmod)
}
 vmod_v0 <- get_vmod_v0()
```


### -1). v0.1 linear regression
```{r}
get_vmod_v0.1 <- function() {
  
  df<- get_train()|>
    select_if(is.numeric)|>
    rename(truth='Premium.Amount')|>
    collect()
  
  rcp <- 
    recipes::recipe(truth ~.,df)|>
    step_rm(all_nominal())|>
    step_impute_median(all_numeric_predictors())|>
    step_rm(id)|>
    step_pca(all_predictors(),num_comp=50)
  
  current_function_name <-
    sys.calls() |>
    as.character()|> 
    gsub('()','',x=_,fixed=T)
  
  vmod <- 
    get_fit_wf(rcp,
               data = df,
               name= current_function_name,
               description='all numeric predictor')
  return(vmod)

}

 vmod_v0.1 <- get_vmod_v0.1()
```

### -2). v0.2 start to use reciep
```{r}

get_vmod_v0.2 <- function(nrows=Inf){
   df<- 
     get_train()|>
     select(all_of(get_colname_by_type('numeric')))|>
    select(-id)|>
    rename(truth='Premium.Amount')|>
    collect()
  
  rcp <- 
    recipes::recipe(truth ~.,df)|>
    step_impute_median(all_numeric_predictors())|>
    step_rm(all_nominal())|>
    step_pca(num_comp=50)
  
    current_function_name <-
    sys.calls() |>
    as.character()|> 
    gsub('()','',x=_,fixed=T)
  
  vmod <- 
    get_fit_wf(rcp,
               data = df,
               name= current_function_name,
               description='fillna to all numeric predictor')
  return(vmod)

}

vmod_v0.2 <- get_vmod_v0.2()

```

### -3). v0.3 start to use recipe

```{r}

get_vmod_v0.3 <- function(nrows=Inf){
  df<- 
    get_train()|>
    select(all_of(c(get_colname_by_type('numeric'),get_colname_by_type('datetime'))))|>
    rename(truth='Premium.Amount')|>
    select(-id)|>
    collect()
  
  rcp <- 
    recipes::recipe(truth ~.,df)|>
    step_date(`Policy.Start.Date`, features = c("dow", "month", "year")) |>
    step_holiday(`Policy.Start.Date`, holidays = timeDate::listHolidays()) |>
    step_rm(`Policy.Start.Date`)|>
    step_impute_median(all_numeric_predictors())|>
    step_rm(all_nominal())|>
    step_pca(num_comp=50)
  

    current_function_name <-
    sys.calls() |>
    as.character()|> 
    gsub('()','',x=_,fixed=T)
  
    vmod <- 
      get_fit_wf(rcp,
                 data = df,
                 name= current_function_name,
                 description='fillna numeric + date feature')
    return(vmod)
  
}
vmod_v0.3 <- get_vmod_v0.3()


```

### -5 v0.5 
```{r}

get_vmod_v0.5 <- function(nrows=Inf){
  df<- 
    get_train()|>
    rename(truth='Premium.Amount')|>
    select(-id)|>
    collect()
  
  rcp <- 
    recipes::recipe(truth ~.,df)|>
    step_date(`Policy.Start.Date`, features = c("dow", "month", "year")) |>
    #step_holiday(`Policy.Start.Date`, holidays = timeDate::listHolidays()) |>
    step_rm(`Policy.Start.Date`)|>
    step_impute_median(all_numeric_predictors())|>
    step_unknown(all_nominal_predictors()) |>
    step_pca(num_comp=50)
  
  current_function_name <-
    sys.calls() |>
    as.character()|> 
    gsub('()','',x=_,fixed=T)
  
    vmod <- 
      get_fit_wf(rcp,
                 data = df,
                 name= current_function_name,
                 description='fillna numeric + date feature+ nominal_dummy_fillmod')
    return(vmod)
  
  
}
# vmod_v0.5 <- get_vmod_v0.5()

```



### -6 v0.6 - manuall change year to dummy 
```{r}

get_vmod_v0.6 <- function(nrows=Inf){
  df<- 
    get_train()|>
    select(-id)|>
    rename(truth='Premium.Amount',
           date = `Policy.Start.Date`)|>
    collect()
  
  rcp <- 
    recipes::recipe(truth ~.,df)|>
    step_date(date, features = c("dow", "month","year")) |>
    step_mutate(date_year = as_factor(date_year)) |>
    step_rm(date)|>
    #step_holiday(`Policy.Start.Date`, holidays = timeDate::listHolidays()) |>
    step_impute_median(all_numeric_predictors())|>
    step_unknown(all_nominal_predictors()) |>
    step_pca(num_comp=50)
  
  
  current_function_name <-
    sys.calls() |>
    as.character()|> 
    gsub('()','',x=_,fixed=T)
  
    vmod <- 
      get_fit_wf(rcp,
                 data = df,
                 name= current_function_name,
                 description='v0.6 fillna numeric + date feature+year nominal_dummy_fillmod')
    return(vmod)
  
}
# vmod_v0.6 <- get_vmod_v0.6()
```

### -7 v0.7 - log1p trans income and claims
```{r}

get_vmod_v0.7 <- function(nrows=Inf){
  df<- 
    get_train()|>
    select(-id)|>
    rename(truth='Premium.Amount',
           date = `Policy.Start.Date`)|>
    collect()
  
   rcp <- 
    recipes::recipe(truth ~.,df)|>
    step_date(date, features = c("dow", "month","year")) |>
    step_rm(date)|>
    #step_holiday(`Policy.Start.Date`, holidays = timeDate::listHolidays()) |>
    step_impute_median(all_numeric_predictors())|>
    step_unknown(all_nominal_predictors()) |>
    step_mutate(date_year = as_factor(date_year),
               Annual.Income=log1p(Annual.Income),
               #Previous.Claims=as_factor(Previous.Claims),
               #Insurance.Duration=as_factor(Insurance.Duration)
               ) |>
    step_nzv()|>
    step_pca(num_comp=50)
  
  
  current_function_name <-
    sys.calls() |>
    as.character()|> 
    gsub('()','',x=_,fixed=T)
  
    vmod <- 
      get_fit_wf(rcp,
                 data = df,
                 name= current_function_name,
                 description='v0.7 mutate income')
    return(vmod)
  
}
# vmod_v0.7 <- get_vmod_v0.7()
```
### -8 v0.8 - log1p trans premium amount
```{r}

get_vmod_v0.8 <- function(nrows=Inf){
  df<- 
    get_train()|>
    select(-id)|>
    rename(truth='Premium.Amount',
           date = `Policy.Start.Date`)|>
    #mutate(truth=log1p(truth))|>
    collect()
  
   rcp <- 
    recipes::recipe(truth ~.,df)|>
    step_log(all_outcomes(), offset = 1,skip=TRUE) |>
    step_date(date, features = c("dow", "month","year")) |>
    step_rm(date)|>
    #step_holiday(`Policy.Start.Date`, holidays = timeDate::listHolidays()) |>
    step_impute_median(all_numeric_predictors())|>
    step_unknown(all_nominal_predictors()) |>
    step_mutate(
      date_year = as_factor(date_year),
      Annual.Income=log1p(Annual.Income),
               ) |>
    step_nzv()|>
    step_pca(num_comp=50)
  
  
  current_function_name <-
    sys.calls() |>
    as.character()|> 
    gsub('()','',x=_,fixed=T)
  
    vmod <- 
      get_fit_wf(rcp,
                 data = df,
                 name= current_function_name,
                 description='v0.8. log1p trans premium amount based on v0.7',
                 is_log1py = TRUE,
                 return_wf = TRUE)
    return(vmod)
  
}
vmod_v0.8 <- get_vmod_v0.8()

```
### -9 v0.9 - add seconds features as the dataset was generated by deeplearning. It is weired.
```{r}

get_vmod_v0.9 <- function(nrows=Inf){
  df<- 
    get_train()|>
    select(-id)|>
    rename(truth='Premium.Amount',
           date = `Policy.Start.Date`)|>
    #mutate(truth=log1p(truth))|>
    collect()
  
   rcp <- 
    recipes::recipe(truth ~.,df)|>
    step_log(all_outcomes(), offset = 1,skip=TRUE) |>
    step_date(date, features = c("dow", "month","year")) |>
    step_time(date, features= c('second'))|>
    step_rm(date)|>
    #step_holiday(`Policy.Start.Date`, holidays = timeDate::listHolidays()) |>
    step_impute_median(all_numeric_predictors())|>
    step_unknown(all_nominal_predictors()) |>
    step_mutate(
      date_year = as_factor(date_year),
      Annual.Income=log1p(Annual.Income),
               ) |>
    step_nzv()|>
    step_pca(num_comp=50)
  
  
  current_function_name <-
    sys.calls() |>
    as.character()|> 
    gsub('()','',x=_,fixed=T)
  
    vmod <- 
      get_fit_wf(rcp,
                 data = df,
                 name= current_function_name,
                 description='v0.9. add seconds feature' ,
                 is_log1py = TRUE,
                 return_wf = TRUE)
    return(vmod)
  
}
# vmod_v0.9 <- get_vmod_v0.9()

```
### -v0.10 - cut some numeric into group
```{r}

get_vmod_v0.10 <- function(nrows = Inf) {
  df <-
    get_train() |>
    rename(truth = 'Premium.Amount', date = `Policy.Start.Date`) |>
    #mutate(truth=log1p(truth))|>
    collect()
  income_pct <- get_train() |> pull(Annual.Income) |> quantile(
    x = _,
    probs = seq(0, 1, 0.2),
    na.rm = TRUE,
    include.lowest = T
  )
  age_pct <- get_train() |> pull(Age) |> quantile(
    x = _,
    probs = seq(0, 1, 0.2),
    na.rm = TRUE,
    include.lowest = T
  )
  date_pct <- get_train()|>pull(Policy.Start.Date)|> quantile(
    x=_, 
    probs=seq(0,1,0.05),
    na.rm = TRUE,
    include.lowest = T
    )
  Credit_pct <- get_train()|>pull(Credit.Score)|> quantile(
    x=_, 
    probs=seq(0,1,0.1),
    na.rm = TRUE,
    include.lowest = T
    )
  Health_pct <- get_train()|>pull(Health.Score)|> quantile(
    x=_, 
    probs=seq(0,1,0.1),
    na.rm = TRUE,
    include.lowest = T
    )
  rcp <-
    recipes::recipe(truth ~ ., df) |>
    update_role(id, new_role='ID')|>
    step_log(all_outcomes(), offset = 1,skip=TRUE) |>
    step_date(date, features = c("dow", "month", "year")) |>
    #    step_time(date, features= c('second'))|>
    #step_holiday(`Policy.Start.Date`, holidays = timeDate::listHolidays()) |>
    step_impute_median(all_numeric_predictors()) |>
    step_unknown(all_nominal_predictors()) |>
    step_mutate(
      Annual.Income_cut = cut(Annual.Income, 
                              breaks = income_pct,
                              include_outside_range = TRUE ),
      Credit.Score_cut = cut(Credit.Score, 
                    breaks = Credit_pct, 
                    include_outside_range = TRUE), 
      Health.Score_cut = cut(Health.Score, 
                    breaks = Health_pct, 
                    include_outside_range = TRUE), 
      Age_cut = cut(Age, 
                    breaks = age_pct, 
                    include_outside_range = TRUE), 
      Age_cut = cut(Age, 
                    breaks = age_pct, 
                    include_outside_range = TRUE), 
      date_cut = cut(date,
                     breaks = date_pct,
                     include_outside_range = TRUE) ) |>
    step_mutate(
      date_year = as_factor(date_year),
      Insurance.Duration = as_factor(Insurance.Duration),
      Previous.Claims = as_factor(Previous.Claims),
      Number.of.Dependents = as_factor(Number.of.Dependents)
      # Annual.Income=log1p(Annual.Income),
    ) |>
    step_nzv() |>
    step_rm(date) |>
    step_pca(num_comp = 50)
  baked_data <- rcp|> prep() |>bake(df)
  
  current_function_name <-
    sys.calls() |>
    as.character() |>
    gsub('()', '', x = _, fixed = T)
  
  vmod <-
    get_fit_wf(
      rcp,
      data = df,
      name = current_function_name,
      description = 'v0.10. add cut age, income',
      is_log1py = TRUE,
      return_wf = TRUE
    )
  return(vmod)
  
}
# vmod_v0.10 <- get_vmod_v0.10()

```
### -v0.11 - cut some numeric into group and convert the group as factor
```{r}

get_vmod_v0.11 <- function(nrows = Inf) {
  df <-
    get_train() |>
    #select(-id) |>
    rename(truth = 'Premium.Amount', date = `Policy.Start.Date`) |>
    #mutate(truth=log1p(truth))|>
    collect()
  
  income_pct <- get_train() |> pull(Annual.Income) |> quantile(
    x = _,
    probs = seq(0, 1, 0.2),
    na.rm = TRUE,
    include.lowest = T
  )
  age_pct <- get_train() |> pull(Age) |> quantile(
    x = _,
    probs = seq(0, 1, 0.2),
    na.rm = TRUE,
    include.lowest = T
  )
  date_pct <- get_train()|>pull(Policy.Start.Date)|> quantile(
    x=_, 
    probs=seq(0,1,0.05),
    na.rm = TRUE,
    include.lowest = T
    )
  Credit_pct <- get_train()|>pull(Credit.Score)|> quantile(
    x=_, 
    probs=seq(0,1,0.1),
    na.rm = TRUE,
    include.lowest = T
    )
  Health_pct <- get_train()|>pull(Health.Score)|> quantile(
    x=_, 
    probs=seq(0,1,0.1),
    na.rm = TRUE,
    include.lowest = T
    )
  
  rcp <-
    recipes::recipe(truth ~ ., df) |>
    update_role(id, new_role='ID')|>
    step_log(all_outcomes(), offset = 1,skip=TRUE) |>
    step_date(date, features = c("dow", "month", "year")) |>
    #    step_time(date, features= c('second'))|>
    #step_holiday(`Policy.Start.Date`, holidays = timeDate::listHolidays()) |>
    step_impute_median(all_numeric_predictors()) |>
    step_unknown(all_nominal_predictors()) |>
    step_mutate(
      Annual.Income_cut = cut(Annual.Income,  breaks = income_pct, include.lowest=TRUE, include_outside_range = TRUE ),
      Credit.Score_cut = cut(Credit.Score,  breaks = Credit_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      Health.Score_cut = cut(Health.Score,  breaks = Health_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      Age_cut = cut(Age,  breaks = age_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      date_cut = cut(date,breaks = date_pct,  include.lowest=TRUE, include_outside_range = TRUE))|>
    step_mutate(
      Annual.Income_cut = as.factor(Annual.Income_cut),
      Credit.Score_cut = as.factor(Credit.Score_cut),
      Health.Score_cut = as.factor(Health.Score_cut),
      Age_cut = as.factor(Age_cut),
      date_cut = as.factor(date_cut),
      date_year = as_factor(date_year),
      Insurance.Duration = as_factor(Insurance.Duration),
      Previous.Claims = as_factor(Previous.Claims),
      Number.of.Dependents = as_factor(Number.of.Dependents)
    ) |>
    step_rm(date) |>
    #step_dummy_hash(all_nominal_predictors(),num_terms=16)|>
    step_nzv() #|>
    #step_pca(all_predictors(),num_comp = 50)
  
  #rcp|>prep()|> print()
 
  current_function_name <-
    sys.calls() |>
    as.character() |>
    gsub('()', '', x = _, fixed = T)
  
  vmod <-
    get_fit_wf(
      rcp,
      data = df,
      name = current_function_name,
      description = 'v0.11. add cut age, income',
      is_log1py = TRUE,
      return_wf = TRUE
    )
  return(vmod)
  
}
# vmod_v0.11 <- get_vmod_v0.11()

```
### -v1.0 - solve the cut include_lowest default value lead to missing data issue 
```{r}

get_vmod_v1.0 <- function(nrows = Inf) {
  df <-
    get_train() |>
    #select(-id) |>
    rename(truth = 'Premium.Amount', date = `Policy.Start.Date`) |>
    #mutate(truth=log1p(truth))|>
    collect()
  
  income_pct <- get_train() |> pull(Annual.Income) |> quantile(
    x = _,
    probs = seq(0, 1, 0.2),
    na.rm = TRUE,
    include.lowest = T
  )
  age_pct <- get_train() |> pull(Age) |> quantile(
    x = _,
    probs = seq(0, 1, 0.2),
    na.rm = TRUE,
    include.lowest = T
  )
  date_pct <- get_train()|>pull(Policy.Start.Date)|> quantile(
    x=_, 
    probs=seq(0,1,0.05),
    na.rm = TRUE,
    include.lowest = T
    )
  Credit_pct <- get_train()|>pull(Credit.Score)|> quantile(
    x=_, 
    probs=seq(0,1,0.1),
    na.rm = TRUE,
    include.lowest = T
    )
  Health_pct <- get_train()|>pull(Health.Score)|> quantile(
    x=_, 
    probs=seq(0,1,0.1),
    na.rm = TRUE,
    include.lowest = T
    )
  
  rcp <-
    recipes::recipe(truth ~ ., df) |>
    update_role(id, new_role='ID')|>
    step_log(all_outcomes(), offset = 1,skip=TRUE) |>
    step_date(date, features = c("dow", "month", "year")) |>
    #    step_time(date, features= c('second'))|>
    #step_holiday(`Policy.Start.Date`, holidays = timeDate::listHolidays()) |>
    step_impute_median(all_numeric_predictors()) |>
    step_unknown(all_nominal_predictors()) |>
    step_mutate(
      Annual.Income_cut = cut(Annual.Income,  breaks = income_pct, include.lowest=TRUE, include_outside_range = TRUE ),
      Credit.Score_cut = cut(Credit.Score,  breaks = Credit_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      Health.Score_cut = cut(Health.Score,  breaks = Health_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      Age_cut = cut(Age,  breaks = age_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      date_cut = cut(date, breaks = date_pct, include.lowest=TRUE,  include_outside_range = TRUE))|>
    step_mutate(
      Annual.Income_cut = as.factor(Annual.Income_cut),
      Credit.Score_cut = as.factor(Credit.Score_cut),
      Health.Score_cut = as.factor(Health.Score_cut),
      Age_cut = as.factor(Age_cut),
      date_cut = as.factor(date_cut),
      date_year = as_factor(date_year),
      Insurance.Duration = as_factor(Insurance.Duration),
      Previous.Claims = as_factor(Previous.Claims),
      Number.of.Dependents = as_factor(Number.of.Dependents)
    ) |>
    step_rm(date) |>
    #step_dummy_hash(all_nominal_predictors(),num_terms=16)|>
    step_nzv() #|>
    #step_pca(all_predictors(),num_comp = 50)
  
  #rcp|>prep()|> print()
 
  current_function_name <-
    sys.calls() |>
    as.character() |>
    gsub('()', '', x = _, fixed = T)
  
  vmod <-
    get_fit_wf(
      rcp,
      data = df,
      name = current_function_name,
      description = 'v1.01',
      is_log1py = TRUE,
      return_wf = TRUE
    )
  return(vmod)
  
}
# vmod_v1.0 <- get_vmod_v1.0()
```


### -v1.01 - as.factor to add more value
```{r}

get_vmod_v1.01 <- function(nrows = Inf) {
    df <-
    get_train() |>
    #select(-id) |>
    rename(truth = 'Premium.Amount', date = `Policy.Start.Date`) |>
    #mutate(truth=log1p(truth))|>
    collect()
  
  income_pct <- get_train() |> pull(Annual.Income) |> quantile(
    x = _,
    probs = seq(0, 1, 0.2),
    na.rm = TRUE,
    include.lowest = T
  )
  age_pct <- get_train() |> pull(Age) |> quantile(
    x = _,
    probs = seq(0, 1, 0.2),
    na.rm = TRUE,
    include.lowest = T
  )
  date_pct <- get_train()|>pull(Policy.Start.Date)|> quantile(
    x=_, 
    probs=seq(0,1,0.05),
    na.rm = TRUE,
    include.lowest = T
    )
  Credit_pct <- get_train()|>pull(Credit.Score)|> quantile(
    x=_, 
    probs=seq(0,1,0.1),
    na.rm = TRUE,
    include.lowest = T
    )
  Health_pct <- get_train()|>pull(Health.Score)|> quantile(
    x=_, 
    probs=seq(0,1,0.1),
    na.rm = TRUE,
    include.lowest = T
    )
  
  rcp <-
    recipes::recipe(truth ~ ., df) |>
    update_role(id, new_role='ID')|>
    step_log(all_outcomes(), offset = 1,skip=TRUE) |>
    step_date(date, features = c("dow", "month", "year")) |>
    #    step_time(date, features= c('second'))|>
    #step_holiday(`Policy.Start.Date`, holidays = timeDate::listHolidays()) |>
    step_impute_median(all_numeric_predictors()) |>
    step_unknown(all_nominal_predictors()) |>
    step_mutate(
      Annual.Income_cut = cut(Annual.Income,  breaks = income_pct, include.lowest=TRUE, include_outside_range = TRUE ),
      Credit.Score_cut = cut(Credit.Score,  breaks = Credit_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      Health.Score_cut = cut(Health.Score,  breaks = Health_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      Age_cut = cut(Age,  breaks = age_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      date_cut = cut(date, breaks = date_pct, include.lowest=TRUE,  include_outside_range = TRUE))|>
    step_mutate(
      Annual.Income_cut = as.factor(Annual.Income_cut),
      Credit.Score_cut = as.factor(Credit.Score_cut),
      Health.Score_cut = as.factor(Health.Score_cut),
      Age_cut = as.factor(Age_cut),
      date_cut = as.factor(date_cut),
      date_year = as_factor(date_year),
      Insurance.Duration = as_factor(Insurance.Duration),
      Previous.Claims = as_factor(Previous.Claims),
      Number.of.Dependents = as_factor(Number.of.Dependents),
      Gender=factor(Gender, levels = c("Male", "Female"), ordered = TRUE),
      Education.Level=factor(Education.Level, levels = c( "High School","Bachelor's","Master's", "PhD"), ordered = TRUE),
      Occupation=factor(Occupation, levels = c("Unemployed","Employed","Self-Employed","NA"), ordered = TRUE),
      Policy.Type=factor(Policy.Type, levels = c("Basic","Comprehensive", "Premium"), ordered = TRUE),
      Customer.Feedback=factor(Customer.Feedback, levels = c("Poor","Average",NA,"Good"), ordered = TRUE),
      Exercise.Frequency=factor(Exercise.Frequency, levels = c("Daily","Weekly",  "Monthly","Rarely"), ordered = TRUE),
      Smoking.Status=factor(Smoking.Status, levels = c("No","Yes"), ordered = TRUE),
      Property.Type=factor(Property.Type, levels = c("Apartment","Condo","House"), ordered = TRUE),
      
    ) |>
    step_rm(date) |>
    #step_dummy_hash(all_nominal_predictors(),num_terms=16)|>
    step_nzv() #|>
    #step_pca(all_predictors(),num_comp = 50)
  
  #rcp|>prep()|> print()
 
  current_function_name <-
    sys.calls() |>
    as.character() |>
    gsub('()', '', x = _, fixed = T)
  
  vmod <-
    get_fit_wf(
      rcp,
      data = df,
      name = current_function_name,
      description = 'v0.11. add cut age, income',
      is_log1py = TRUE,
      return_wf = TRUE
    )
  return(vmod)
  
}
# vmod_v1.01 <- get_vmod_v1.01()
```
### -v1.02b - add grp_col featuure which as seqency id and log1p annual income
```{r}

get_vmod_v1.02b <- function(nrows = Inf) {
  df <-get_train()
  
  result_pct <- df|> get_cut_pct()
  grp_col <- df |>get_grp_feature()
  
  df <-
    df |>
    #select(-id) |>
    rename(truth = 'Premium.Amount', date = `Policy.Start.Date`) |>
    #mutate(truth=log1p(truth))|>
    collect()

  df<-
    df|>
    left_join(grp_col,by='id')
  
  rcp <-
    recipes::recipe(truth ~ ., df) |>
    update_role(id, new_role='ID')|>
    step_log(all_outcomes(), offset = 1,skip=TRUE) |>
    step_date(date, features = c("dow", "month", "year")) |>
    #    step_time(date, features= c('second'))|>
    #step_holiday(`Policy.Start.Date`, holidays = timeDate::listHolidays()) |>

    step_mutate(
      Annual.Income_cut = cut(Annual.Income,  breaks = result_pct$income_pct, include.lowest=TRUE, include_outside_range = TRUE ),
      Credit.Score_cut = cut(Credit.Score,  breaks = result_pct$Credit_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      Health.Score_cut = cut(Health.Score,  breaks = result_pct$Health_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      Age_cut = cut(Age,  breaks = result_pct$age_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      date_cut = cut(date, breaks = result_pct$date_pct, include.lowest=TRUE,  include_outside_range = TRUE))|>
    step_mutate(
      Annual.Income_cut = as.factor(Annual.Income_cut),
      Credit.Score_cut = as.factor(Credit.Score_cut),
      Health.Score_cut = as.factor(Health.Score_cut),
      Age_cut = as.factor(Age_cut),
      date_cut = as.factor(date_cut),
      date_year = as_factor(date_year),
      Insurance.Duration = as_factor(Insurance.Duration),
      Previous.Claims = as_factor(Previous.Claims),
      Number.of.Dependents = as_factor(Number.of.Dependents),
      Gender=factor(Gender, levels = c("Male", "Female"), ordered = TRUE),
      Education.Level=factor(Education.Level, levels = c( "High School","Bachelor's","Master's", "PhD"), ordered = TRUE),
      Occupation=factor(Occupation, levels = c("Unemployed","Employed","Self-Employed","NA"), ordered = TRUE),
      Policy.Type=factor(Policy.Type, levels = c("Basic","Comprehensive", "Premium"), ordered = TRUE),
      Customer.Feedback=factor(Customer.Feedback, levels = c("Poor","Average",NA,"Good"), ordered = TRUE),
      Exercise.Frequency=factor(Exercise.Frequency, levels = c("Daily","Weekly",  "Monthly","Rarely"), ordered = TRUE),
      Smoking.Status=factor(Smoking.Status, levels = c("No","Yes"), ordered = TRUE),
      Property.Type=factor(Property.Type, levels = c("Apartment","Condo","House"), ordered = TRUE),

    ) |>
    step_impute_median(all_numeric_predictors()) |>
    step_log(Annual.Income,offset = 1)|>
    step_unknown(all_nominal_predictors()) |>
    step_rm(date) |>
    step_nzv(all_numeric_predictors()) |>
    step_pca(all_numeric_predictors(),num_comp = 50) |>
    check_missing(all_predictors())
  
  current_function_name <-
    sys.calls() |>
    as.character() |>
    gsub('()', '', x = _, fixed = T)
  
  vmod <-
    get_fit_wf(
      rcp,
      data = df,
      name = current_function_name,
      description = 'v1.02 add grouped feature',
      is_log1py = TRUE,
      return_wf = TRUE
    )
  return(vmod)
  
}
vmod_v1.02b <- get_vmod_v1.02b()
```
### -v1.03cut - add grp_col featuure and seconds features add microsecond feature
```{r}

get_vmod_v1.03_cut <- function(nrows = Inf) {
  
 df<-
    get_train() |>
    get_enrich_df()
  
  rcp <-
    recipes::recipe(truth ~ ., df) |>
    step_log(all_outcomes(), offset = 1,skip=TRUE) |>
    update_role(id, new_role='ID')|>
#    step_date(date, features = c("dow", "month", "year")) |>
    step_impute_median(all_numeric_predictors()) |>
    #step_time(date, features= c('second'))|>
    #step_holiday(`Policy.Start.Date`, holidays = timeDate::listHolidays()) |>
    #step_mutate(
      #Annual.Income_cut = cut(log1p(Annual.Income),  breaks = result_pct$income_pct, include.lowest=TRUE, include_outside_range = TRUE ),
      #Credit.Score_cut = cut(Credit.Score,  breaks = result_pct$Credit_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      #Health.Score_cut = cut(Health.Score,  breaks = result_pct$Health_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      #Age_cut = cut(Age,  breaks = result_pct$age_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      #microsecond_cut = cut(microsecond,  breaks = result_pct$microsecond_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      #date_cut = cut(date, breaks = result_pct$date_pct, include.lowest=TRUE,  include_outside_range = TRUE))|>
    step_integer(date)|>
    step_mutate(Annual.Income.Raw=Annual.Income)|>
    step_discretize(Annual.Income, date, num_breaks =20) |>
    step_discretize(Credit.Score,Health.Score,Age, num_breaks=10) |>
    step_discretize(microsecond,  num_breaks =10)|>
    step_mutate(
      # Annual.Income_cut = as.factor(Annual.Income_cut),
      # Credit.Score_cut = as.factor(Credit.Score_cut),
      # Health.Score_cut = as.factor(Health.Score_cut),
      # Age_cut = as.factor(Age_cut),
      # microsecond_cut = as.factor(microsecond_cut),
      # date_cut = as.factor(date_cut),
      date_year = as_factor(year),
      Insurance.Duration = as_factor(Insurance.Duration),
      Previous.Claims = as_factor(Previous.Claims),
      Number.of.Dependents = as_factor(Number.of.Dependents),
      Gender=factor(Gender, levels = c("Male", "Female"), ordered = TRUE),
      Education.Level=factor(Education.Level, levels = c( "High School","Bachelor's","Master's", "PhD"), ordered = TRUE),
      Occupation=factor(Occupation, levels = c("Unemployed","Employed","Self-Employed","NA"), ordered = TRUE),
      Policy.Type=factor(Policy.Type, levels = c("Basic","Comprehensive", "Premium"), ordered = TRUE),
      Customer.Feedback=factor(Customer.Feedback, levels = c("Poor","Average",NA,"Good"), ordered = TRUE),
      Exercise.Frequency=factor(Exercise.Frequency, levels = c("Daily","Weekly",  "Monthly","Rarely"), ordered = TRUE),
      Smoking.Status=factor(Smoking.Status, levels = c("No","Yes"), ordered = TRUE),
      Property.Type=factor(Property.Type, levels = c("Apartment","Condo","House"), ordered = TRUE)
    ) |>
    step_unknown(all_nominal_predictors()) |>
    step_log(Annual.Income.Raw,offset = 1)|>
    step_rm(date) |>
    step_nzv(all_predictors()) |>
#    step_corr(all_numeric_predictors(), threshold = 0.8)|>
    step_pca(all_numeric_predictors(),num_comp = 50) 
    #check_missing(all_predictors())
  
  #rcp|>summary()
  
  current_function_name <-
    sys.calls() |>
    as.character() |>
    gsub('()', '', x = _, fixed = T)
  
  vmod <-
    get_fit_wf(
      rcp,
      data = df,
      name = current_function_name,
      description = 'v1.03_cut',
      is_log1py = TRUE,
      return_wf =TRUE 
    )
  return(vmod)
  
}
vmod_v1.03_cut<- get_vmod_v1.03_cut()
```



### -v1.1 feature engineering on microsecond and year which as cosine period relation
```{r}


get_vmod_v1.1 <- function(nrows = Inf) {
  df <-get_train()
  
  result_pct <- df|> get_cut_pct()
  grp_col <- df |>get_grp_feature()
  
  df<-
    df|>get_enrich_df()
  
  rcp <-
    recipes::recipe(truth ~ ., df) |>
    step_log(all_outcomes(), offset = 1,skip=TRUE) |>
    update_role(id, new_role='ID')|>
    step_mutate(sin_ms = sin(2*pi * microsecond),
                cos_ms = cos(2*pi * microsecond),
                inv_year_ms =year * microsecond,
                angle_theta = atan2(year, microsecond),  # Angle
                magnitude = sqrt(year**2 + microsecond**2)  # Magnitude
    )|>

    #step_holiday(`Policy.Start.Date`, holidays = timeDate::listHolidays()) |>

    step_mutate(
      Annual.Income_cut = cut(log1p(Annual.Income),  breaks = result_pct$income_cut, include.lowest=TRUE, include_outside_range = TRUE ),
      Credit.Score_cut = cut(Credit.Score,  breaks = result_pct$Credit_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      Health.Score_cut = cut(Health.Score,  breaks = result_pct$Health_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      Age_cut = cut(Age,  breaks = result_pct$age_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      microsecond_cut = cut(microsecond,  breaks = result_pct$microsecond_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      date_cut = cut(date, breaks = result_pct$date_pct, include.lowest=TRUE,  include_outside_range = TRUE))|>
    step_mutate(
      Annual.Income_cut = as.factor(Annual.Income_cut),
      Credit.Score_cut = as.factor(Credit.Score_cut),
      Health.Score_cut = as.factor(Health.Score_cut),
      Age_cut = as.factor(Age_cut),
      microsecond_cut = as.factor(microsecond_cut),
      date_cut = as.factor(date_cut),
      date_year = as_factor(year),
      Insurance.Duration = as_factor(Insurance.Duration),
      Previous.Claims = as_factor(Previous.Claims),
      Number.of.Dependents = as_factor(Number.of.Dependents),
      Gender=factor(Gender, levels = c("Male", "Female"), ordered = TRUE),
      Education.Level=factor(Education.Level, levels = c( "High School","Bachelor's","Master's", "PhD"), ordered = TRUE),
      Occupation=factor(Occupation, levels = c("Unemployed","Employed","Self-Employed","NA"), ordered = TRUE),
      Policy.Type=factor(Policy.Type, levels = c("Basic","Comprehensive", "Premium"), ordered = TRUE),
      Customer.Feedback=factor(Customer.Feedback, levels = c("Poor","Average",NA,"Good"), ordered = TRUE),
      Exercise.Frequency=factor(Exercise.Frequency, levels = c("Daily","Weekly",  "Monthly","Rarely"), ordered = TRUE),
      Smoking.Status=factor(Smoking.Status, levels = c("No","Yes"), ordered = TRUE),
      Property.Type=factor(Property.Type, levels = c("Apartment","Condo","House"), ordered = TRUE),
    ) |>
  
    step_impute_median(all_numeric_predictors()) |>
    step_unknown(all_nominal_predictors()) |>
   step_log(Annual.Income,offset = 1)|>
    step_rm(date) |>
    step_nzv(all_predictors()) |>
    step_pca(all_numeric_predictors(),num_comp = 50) 
    #check_missing(all_predictors())
  
  #rcp|>summary()
  
  current_function_name <-
    sys.calls() |>
    as.character() |>
    gsub('()', '', x = _, fixed = T)
  print('start training') 
  vmod <-
    get_fit_wf(
      rcp,
      data = df,
      name = current_function_name,
      description = '1.1. based on v1.03 add grouped feature & seconds feature',
      is_log1py = TRUE,
      return_wf =FALSE 
    )
  return(vmod)
  
}
vmod_v1.1<- get_vmod_v1.1()
```

### -v1.04 - using lightgbm
```{r}

get_vmod_v1.04 <- function(nrows = Inf) {
  df <-get_train()
  
  #result_pct <- df|> get_cut_pct()
  grp_col <- df |>get_grp_feature()
  
  df<-
    df|>get_enrich_df()
  
  rcp <-
    recipes::recipe(truth ~ ., df) |>
    step_log(all_outcomes(), offset = 1,skip=TRUE) |>
    update_role(id, new_role='ID')|>
    #step_date(date, features = c("dow", "month", "year")) |>
    #step_time(date, features= c('second'))|>
    #step_holiday(`Policy.Start.Date`, holidays = timeDate::listHolidays()) |>
    step_mutate(
      Annual.Income_cut = cut(Annual.Income,  breaks = result_pct$income_pct, include.lowest=TRUE, include_outside_range = TRUE ),
      Credit.Score_cut = cut(Credit.Score,  breaks = result_pct$Credit_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      Health.Score_cut = cut(Health.Score,  breaks = result_pct$Health_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      Age_cut = cut(Age,  breaks = result_pct$age_pct,  include.lowest=TRUE, include_outside_range = TRUE ),
      date_cut = cut(date, breaks = result_pct$date_pct, include.lowest=TRUE,  include_outside_range = TRUE))|>
    step_mutate(
      Annual.Income_cut = as.factor(Annual.Income_cut),
      Credit.Score_cut = as.factor(Credit.Score_cut),
      Health.Score_cut = as.factor(Health.Score_cut),
      Age_cut = as.factor(Age_cut),
      date_cut = as.factor(date_cut),
      Insurance.Duration = as_factor(Insurance.Duration),
      Previous.Claims = as_factor(Previous.Claims),
      Number.of.Dependents = as_factor(Number.of.Dependents),
      Gender=factor(Gender, levels = c("Male", "Female"), ordered = TRUE),
      Education.Level=factor(Education.Level, levels = c( "High School","Bachelor's","Master's", "PhD"), ordered = TRUE),
      Occupation=factor(Occupation, levels = c("Unemployed","Employed","Self-Employed","NA"), ordered = TRUE),
      Policy.Type=factor(Policy.Type, levels = c("Basic","Comprehensive", "Premium"), ordered = TRUE),
      Customer.Feedback=factor(Customer.Feedback, levels = c("Poor","Average",NA,"Good"), ordered = TRUE),
      Exercise.Frequency=factor(Exercise.Frequency, levels = c("Daily","Weekly",  "Monthly","Rarely"), ordered = TRUE),
      Smoking.Status=factor(Smoking.Status, levels = c("No","Yes"), ordered = TRUE),
      Property.Type=factor(Property.Type, levels = c("Apartment","Condo","House"), ordered = TRUE),
    ) |>
    step_integer(all_nominal_predictors()) |>
    step_impute_median(all_numeric_predictors()) |>
    step_unknown(all_nominal_predictors()) |>
    step_log(Annual.Income,offset=1)|>
    step_rm(date) |>
    step_nzv(all_predictors()) |>
    #step_pca(all_numeric_predictors(),num_comp = 100)|>
    step_corr(all_numeric_predictors(),threshold = 0.9)|>
    check_missing(all_predictors())
  # print('checking baked rcp') 
  #  baked_df<-  rcp|>prep()|>bake(df|>head(10000)) 
  #  baked_df <- NULL 
  # print('check rcp done!')
  current_function_name <-
    sys.calls() |>
    as.character() |>
    gsub('()', '', x = _, fixed = T)
  # 
  # 
  # 
 
  # fit_mod <- 
  #   fit_wf |> 
  #   extract_fit_engine()
  # 
  # lgb_wf <- get_lgb_wf(n_trees=3000,n_depth = 15, rate=0.01,n_leaves=2048, n_leaves_min=20,min_gain_to_split=0.0001)
  # fit_wf <- lgb_wf |>
  #   add_recipe(rcp)|>
  #   fit(data = df)
  # return(fit_wf)
  # 
  # fit_mod <- 
  #   fit_wf |> 
  #   extract_fit_engine()
  print('start training') 
  vmod <-
    get_fit_lgbwf(
      rcp,
      data = df,
      name = current_function_name,
      description = 'v1.04 lightgbm with v1.03 feature',
      is_log1py = TRUE,
      return_wf = TRUE,
      tree_depth=40
    )
  return(vmod)
  
}
vmod_v1.04 <- get_vmod_v1.04()

```

### - v1.x
```{r}
# TODO Annual income need keep
# current import features are : health score, Annual.Income_cut, Credit.Score_cut, mean_income, mean_age, microsecond, first, last, weekly_cnt, avg, looks the feature engineering has many things to do.

#DONE know why some insurance premium amount was so low - Annaul income is very important
#DONE 20 price buying pattern related to time. False. everyday. happened. it related to group people. 
#DONE The answer is no. Is there pattern that, group by high price insuance first and then buy low price. later. It may related to time series .2019-early of 2020 is very high.  and people

# DONE the dataset was generated by deep learning process. find the pattern. continue. it break down to several new.

# DONE use decision tree or forest to eda. plot tree showed Annual income is key.


# DONE-skip. add null count per row variable. recipe has no such built in feature
# DONE-skip modify miss na with group instead of whole. recipe not support
# Done-still build user group identity and find if they buy some insurance.
# Done-skip add daily total,avg , mean ,sd based on train basedon group 
# DONE - add sequency id
# DONE - the Premium Amount first digit 4,5,6,7,8,9 do not follow ben ford role. when ding sampling, it should be considered.
# DONE - skip. publish notebook

```


### - v1.1 workflowset
```{r}
best_mod <-

```

## 2.3 vetiver
## version model

```{r}
show_model_permformance() %>% 
  filter(grepl('vmod',id) & .estimate <1.1)|>
  mutate(id=fct_reorder(id,desc(.estimate))) %>%
  ggplot(aes(x=id,xend=id,y = 1.0, yend=.estimate,fill=id)) +
  geom_segment(size=7,color='blue')+
  geom_text(aes(x = id, y = .estimate, label = .estimate), 
            hjust = -0.2, vjust = 0.5, size = 5, color = "red") +
  #geom_hline(yintercept = .estimate) +
  scale_y_continuous(limits=c(0.8,1.10),
                     #breaks= seq(0.8, 1.2,by = 0.1)
                     )+
  labs (title = 'model performance board',
        color=NULL) +
  coord_flip()+
  theme_gray()
  
```


## 2.4 plot residual

## plot residual
```{r}

 
  get_mods_log_residual(mod_name_pattern = 'v1.03_cut|v1.1|v1.04')|>
  ggplot(aes(x = value, fill = name,color=name)) +
  geom_density(alpha = 0.1) +
  labs(title = "Overlaid Density Plots", x = "Values", y = "Density") +
  theme_minimal()
  
```

```{r}
get_train()|>
  select(id,date=`Policy.Start.Date`) |>
  cbind(get_mods_log_residual(mod_name_pattern = 'v0.8')) |>
  group_by(year(date)) |>
  summarize(across(starts_with('value'),
                   list(mean = ~ mean(.x, na.rm = TRUE),
                        sum = ~sum(.x,na.rm = T)
                        ), 
                   .names = "{.col}.{.fn}")
            ) |>
  round(2)


```

```{r}
year_log_resi <- 
  get_train()|>select(id,date=`Policy.Start.Date`) |>
  cbind(get_mods_log_residual(mod_name_pattern = 'v0.8')|>filter(grepl('v0.8',name))) |> mutate(year_id = as_factor(year(date))) 

year_log_resi|>
  select(value, year=year_id)|>
  ggplot(aes(x = value, group=year,color = year)) +
  geom_density(alpha = 0.3)+
    labs(title = "Overlaid Density Plots", x = "Values", y = "Density") +
  theme_minimal()

```
# 3. predict and submit
by use trained work flow to predict and submit
```{r}
best_mod <- vmod_v1.03_cut
save_submit <-function(best_mod ){
  
  submit_file_name <- 'output/sample_submit.csv_v1.03_cut.gz'
  
  df <-get_test()
  
  result_pct <- df|> get_cut_pct()
  grp_col <- df |>get_grp_feature()
  
  df<-
    df|>get_enrich_df()

  pred <- best_mod|>
    predict(df)|>
    pull(.pred)
  
  get_sample() |>
    select(id) |>
    collect()|>
    mutate(`Premium Amount` = exp(pred)-1)|>
    fwrite(submit_file_name,compress='gzip')
}

save_submit(best_mod)
```



### eda rpart tree plot 
```{r}
library(tidymodels)
library(rpart.plot)
library(vip)


get_rpart_plot <- function() {
  tree_spec <-
    decision_tree(cost_complexity = 0.001,
                  min_n = 100,
                  tree_depth = 8) |>
    set_engine("rpart", model = TRUE)
  
  reg_tree_spec <-
    tree_spec |>
    set_mode("regression")
  
  set.seed(1234)
  
  df <-
    get_train() |>
    #select(-id) |>
    rename(truth = 'Premium.Amount', date = `Policy.Start.Date`) |>
    #mutate(truth=log1p(truth))|>
    collect()
  
  income_pct <- get_train() |> pull(Annual.Income) |> quantile(
    x = _,
    probs = seq(0, 1, 0.2),
    na.rm = TRUE,
    include.lowest = T
  )
  age_pct <- get_train() |> pull(Age) |> quantile(
    x = _,
    probs = seq(0, 1, 0.2),
    na.rm = TRUE,
    include.lowest = T
  )
  date_pct <- get_train() |> pull(Policy.Start.Date) |> quantile(
    x = _,
    probs = seq(0, 1, 0.05),
    na.rm = TRUE,
    include.lowest = T
  )
  Credit_pct <- get_train() |> pull(Credit.Score) |> quantile(
    x = _,
    probs = seq(0, 1, 0.1),
    na.rm = TRUE,
    include.lowest = T
  )
  Health_pct <- get_train() |> pull(Health.Score) |> quantile(
    x = _,
    probs = seq(0, 1, 0.1),
    na.rm = TRUE,
    include.lowest = T
  )
  
  rcp <-
    recipes::recipe(truth ~ ., df) |>
    update_role(id, new_role = 'ID') |>
    step_log(all_outcomes(), offset = 1,skip=TRUE) |>
    step_date(date, features = c("dow", "month", "year")) |>
    #    step_time(date, features= c('second'))|>
    #step_holiday(`Policy.Start.Date`, holidays = timeDate::listHolidays()) |>
    step_impute_median(all_numeric_predictors()) |>
    step_unknown(all_nominal_predictors()) |>
    step_mutate(
      Annual.Income_cut = cut(
        Annual.Income,
        breaks = income_pct,
        include.lowest = TRUE,
        include_outside_range = TRUE
      ),
      Credit.Score_cut = cut(
        Credit.Score,
        breaks = Credit_pct,
        include.lowest = TRUE,
        include_outside_range = TRUE
      ),
      Health.Score_cut = cut(
        Health.Score,
        breaks = Health_pct,
        include.lowest = TRUE,
        include_outside_range = TRUE
      ),
      Age_cut = cut(
        Age,
        breaks = age_pct,
        include.lowest = TRUE,
        include_outside_range = TRUE
      ),
      date_cut = cut(
        date,
        breaks = date_pct,
        include.lowest = TRUE,
        include_outside_range = TRUE
      )
    ) |>
    step_mutate(
      Annual.Income_cut = as.factor(Annual.Income_cut),
      Credit.Score_cut = as.factor(Credit.Score_cut),
      Health.Score_cut = as.factor(Health.Score_cut),
      Age_cut = as.factor(Age_cut),
      date_cut = as.factor(date_cut),
      date_year = as_factor(date_year),
      Insurance.Duration = as_factor(Insurance.Duration),
      Previous.Claims = as_factor(Previous.Claims),
      Number.of.Dependents = as_factor(Number.of.Dependents),
      Gender = factor(
        Gender,
        levels = c("Male", "Female"),
        ordered = TRUE
      ),
      Education.Level = factor(
        Education.Level,
        levels = c("High School", "Bachelor's", "Master's", "PhD"),
        ordered = TRUE
      ),
      Occupation = factor(
        Occupation,
        levels = c("Unemployed", "Employed", "Self-Employed", "NA"),
        ordered = TRUE
      ),
      Policy.Type = factor(
        Policy.Type,
        levels = c("Basic", "Comprehensive", "Premium"),
        ordered = TRUE
      ),
      Customer.Feedback = factor(
        Customer.Feedback,
        levels = c("Poor", "Average", NA, "Good"),
        ordered = TRUE
      ),
      Exercise.Frequency = factor(
        Exercise.Frequency,
        levels = c("Daily", "Weekly", "Monthly", "Rarely"),
        ordered = TRUE
      ),
      Smoking.Status = factor(
        Smoking.Status,
        levels = c("No", "Yes"),
        ordered = TRUE
      ),
      Property.Type = factor(
        Property.Type,
        levels = c("Apartment", "Condo", "House"),
        ordered = TRUE
      ),
      
    ) |>
    step_rm(date) |>
    #step_dummy_hash(all_nominal_predictors(),num_terms=16)|>
    step_nzv() |>
    prep() |> bake(new_data = df)
  
  
  reg_tree_fit <- fit(reg_tree_spec, truth ~ ., rcp)
  reg_tree_fit %>%
    extract_fit_engine() %>%
    rpart.plot()
  
  
}
get_rpart_plot()

```

